---
title: "Overview of Your Study Experiences"
output:
  word_document:
    reference_docx: "template_comp.docx"
  html_document: default
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	dpi = 600
)
# Load required libraries
library(wordcloud)
library(RColorBrewer)
library(tm)
library(ggplot2)
library(tidyr)
library(dplyr)

library(patchwork)
library(stringr)
library(lubridate)
library(RPostgres)


participant <- Sys.getenv("PARTICIPANT_NUMBER", NA)

# Read environment variables (with defaults)
DB_USER <- Sys.getenv("DB_USER", "hannah")
DB_PASSWORD <- Sys.getenv("DB_PASSWORD", "moodtriggers2025")
DB_HOST <- Sys.getenv("DB_HOST", "localhost")
DB_PORT <- Sys.getenv("DB_PORT", "5432")
DB_NAME <- Sys.getenv("DB_NAME", "moodtriggers")

# Connect to PostgreSQL database
con <- dbConnect(
  RPostgres::Postgres(),
  user = DB_USER,
  password = DB_PASSWORD,
  host = DB_HOST,
  port = DB_PORT,
  dbname = DB_NAME
)

# Load tables
weekly <- dbReadTable(con, "weekly_data")

#weekly <- read.csv("weekly_raw__data_plot.csv")
weekly <- weekly[weekly$record_id == participant, ]

weekly <- weekly[weekly$w_timestamp != "[not completed]", ]

#daily <- read.csv(paste0("ema_response/",participant,"_ema_response.csv"))
daily <- dbReadTable(con, "ema_responses_final3")
daily <- daily[daily$participant_id == participant, ]

daily <- daily[!is.na(daily$timestamp),]
#daily_extra <- read.csv(paste0("ema_response/",participant_extra,"_ema_response.csv"))
#daily_extra2 <- read.csv(paste0("ema_response/",participant_extra2,"_ema_response.csv"))

#daily = rbind(daily,daily_extra)
#daily = rbind(daily,daily_extra,daily_extra2)

color1 = "#00331A" # ratings per time
color2 = "#00331A" # ratings per time

color3 = "#CBA135" #line

df <- daily %>%
  mutate(ema_category = case_when(
    # Negative symptoms
    grepl("I would rather have been doing something else\\.", questionText) ~ "Negative symptom",
    grepl("I have felt unmotivated\\.", questionText) ~ "Negative symptom",
    grepl("I have felt emotionally flat, numb, or blank\\.", questionText) ~ "Negative symptom",
    grepl("I have experienced difficulty expressing my emotions or thoughts\\.", questionText) ~ "Negative symptom",
    grepl("I have not wanted to socialize\\.", questionText) ~ "Negative symptom",

    # Positive symptoms
    grepl("to what degree have you had any unusual experiences\\?", questionText) ~ "Positive symptom",
    grepl("I have felt detached from reality\\.", questionText) ~ "Positive symptom",
    grepl("I have felt I possess special powers or abilities\\.", questionText) ~ "Positive symptom",
    grepl("I have felt I am receiving special messages\\.", questionText) ~ "Positive symptom",
    grepl("I have felt suspicious of others\\.", questionText) ~ "Positive symptom",

    # Cognitive symptoms
    grepl("I have found it easy to concentrate\\.", questionText) ~ "Cognitive symptom",
    grepl("I have experienced racing thoughts\\.", questionText) ~ "Cognitive symptom",
    grepl("I have found it easy to make decisions\\.", questionText) ~ "Cognitive symptom",
    grepl("I have experienced difficulty thinking clearly\\.", questionText) ~ "Cognitive symptom",
    grepl("I have had trouble remembering things\\.", questionText) ~ "Cognitive symptom",

    # Functional outcomes
    grepl("I have been able to complete my daily activities\\.", questionText) ~ "Functional outcome",
    grepl("I have been able to interact with others\\.", questionText) ~ "Functional outcome",
    grepl("I have been able to manage my physical and mental health\\.", questionText) ~ "Functional outcome",

    # Suicide ideation and follow-up
    grepl("I had had thoughts of hurting myself or that I would be better off dead\\.", questionText) ~ "Suicide ideation/self-harm",
    grepl("Do you intend to end your life now or in the near future\\?", questionText) ~ "Suicide risk follow-up",

    # Sleep quality
    grepl("Last night I had trouble with sleep\\.", questionText) ~ "Sleep quality",

    # Medication adherence
    grepl("I took my medications for psychotic symptoms today\\.", questionText) ~ "Medication adherence",

    # Default case
    TRUE ~ NA_character_
  ))

# Filter out unwanted categories
df_filtered <- df %>%
  filter(
    !ema_category %in% c("Medication adherence", "Suicide ideation/self-harm"),
    !is.na(ema_category)
  ) %>%
  mutate(response = as.numeric(response))

# Compute mean response for each individual item
item_means <- df_filtered %>%
  group_by(questionText, ema_category) %>%
  summarise(mean_response = mean(response, na.rm = TRUE), .groups = "drop")

```

# What This Report Shows

Thank you for participating in this study. This report summarizes what
you shared with us about your experiences, feelings, symptoms, and daily
life over the weeks. **There are no right or wrong answers**.

## 📆 Daily Questionnaires

Here, you will see a summary of the answers you provided in the **daily
questionnaires**, which you completed **three times a day for 90 days**.

```{r echo=FALSE, fig.height=6.5, fig.width=11.5, message=FALSE, warning=FALSE}

create_time_plots <- function(outcome) {

  df_symptom = df_filtered[df_filtered$ema_category == outcome, ]
  
  df_symptom <- df_symptom %>%
    mutate(
      date = as.POSIXct(date),
      day_type = weekdays(date),
      hour = hour(date),
      time_of_day = case_when(
        hour >= 5 & hour < 12 ~ "Morning (5:00 AM - 11:59 AM)",
        hour >= 12 & hour < 17 ~ "Afternoon (12:00 PM - 4:59 PM)",
        hour >= 17 & hour < 24 ~ "Evening (5:00 PM - 11:59 PM)",
        hour >= 0 & hour < 5 ~ "Night (12:00 AM - 4:59 AM)"
      )
    )
  
  # Calculate means by day type and time of day
  summary_data_time <- df_symptom %>%
    group_by(time_of_day) %>%
    summarise(mean_response = mean(as.numeric(response), na.rm = TRUE), .groups = "drop")
  
  summary_data_time$time_of_day <- factor(summary_data_time$time_of_day, ordered = TRUE,
                                          levels = c("Morning (5:00 AM - 11:59 AM)", "Afternoon (12:00 PM - 4:59 PM)", "Evening (5:00 PM - 11:59 PM)","Night (12:00 AM - 4:59 AM)"))
  
  summary_data_day <- df_symptom %>%
    group_by(day_type) %>%
    summarise(mean_response = mean(as.numeric(response), na.rm = TRUE), .groups = "drop")
  
  summary_data_day$day_type <- factor(summary_data_day$day_type, ordered = TRUE,
                                      levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
  
  # Plot by time of day
  a = ggplot(summary_data_time, aes(x = time_of_day, y = mean_response)) +
    geom_bar(stat = "identity", position = "dodge", fill = color1) +
    geom_text(aes(label = round(mean_response, 1)), vjust = -0.5, size = 5) +  # Add mean labels
    scale_y_continuous(limits = c(0, 100)) +
    labs(
      title = "Average Ratings by Time of Day",
      x = "",
      y = ""
    ) +
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(face = "bold", size = 16),
      axis.text = element_text(size = 14),
      axis.title = element_text(size = 14),
      legend.position = "right"
    )
  
  # Plot by weekday
  b = ggplot(summary_data_day, aes(x = day_type, y = mean_response)) +
    geom_bar(stat = "identity", position = "dodge", fill = color1) +
    geom_text(aes(label = round(mean_response, 1)), vjust = -0.5, size = 5) +  # Add mean labels
    scale_y_continuous(limits = c(0, 100)) +
    labs(
      title = "Average Ratings by Weekday",
      x = "",
      y = ""
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(face = "bold", size = 16),
      axis.text = element_text(size = 14),
      axis.title = element_text(size = 14),
      legend.position = "right"
    )
  
  plot = a / b  # Weekday plot on top, time of day on bottom
  return(plot)
}



category_means <- df_filtered %>%
  filter(!is.na(ema_category)) %>%
  mutate(
    date  = as.Date(date)          
  ) %>%
  group_by(date, ema_category) %>%
  summarise(
    mean_response = mean(as.numeric(response), na.rm = TRUE),
    .groups = "drop"
  )

category_means <- category_means %>%
  mutate(date = as.POSIXct(date))


a = ggplot(category_means[category_means$ema_category == "Positive symptom",], aes(x = date, y = mean_response, color = color2)) +
  scale_color_manual(values = color2) +
  geom_line() +
  scale_y_continuous(
    limits = c(0, 100)
  ) +
  labs(
    title = "Variation Over Time (Average per Day)",
    y = "",
    x = ""
  ) +
  theme_minimal() +
   theme(
      plot.title = element_text(face = "bold", size = 16),
      axis.text = element_text(size = 14),
      axis.title = element_text(size = 14),
      legend.position = "none"
    )

b = create_time_plots("Positive symptom")

(b/a) +
  plot_layout(heights = c(1, 1,1)) +
  plot_annotation(
    title = "Positive Symptoms",
    subtitle = "Like suspicion of others, receiving special messages, special powers, or detachment from reality.",
    caption = "0 = Not at all, 100 = Constantly",
    theme = theme(
      plot.title = element_text(size = 18, face = "bold"),
      plot.subtitle = element_text(size = 14),
      plot.caption = element_text(size = 14)
    )
  )

```

#### Average Ratings by Question (Over the Past 4 Hours)

```{r echo=FALSE, fig.height=3, fig.width=11.5, message=FALSE, warning=FALSE}
item_means$questionText <- stringr::str_to_sentence((gsub("^In the past 4 hours, ", "", item_means$questionText)))

ggplot(item_means[item_means$ema_category == "Positive symptom",], 
       aes(x = reorder(questionText, mean_response), y = mean_response)) +
  geom_col(width = 0.6, fill = color3) +
  coord_flip() +
  labs(
    x = NULL,
    y = ""
  ) +
  ylim(c(0, 100)) +
  theme_minimal() +
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 16),
    legend.position = "none"
  )


```

```{r echo=FALSE, fig.height=6.5, fig.width=11.5, message=FALSE, warning=FALSE}

category_means <- df_filtered %>%
  filter(!is.na(ema_category)) %>%
  mutate(
    date  = as.Date(date)          
  ) %>%
  group_by(date, ema_category) %>%
  summarise(
    mean_response = mean(as.numeric(response), na.rm = TRUE),
    .groups = "drop"
  )

category_means <- category_means %>%
  mutate(date = as.POSIXct(date))


a = ggplot(category_means[category_means$ema_category == "Negative symptom",], aes(x = date, y = mean_response, color = color2)) +
  geom_line() +
  scale_color_manual(values = color2) +
  scale_y_continuous(
    limits = c(0, 100)
  ) +
  labs(
    title = "Variation Over Time (Average per Day)",
    y = "",
    x = ""
  ) +
  theme_minimal() +
   theme(
      plot.title = element_text(face = "bold", size = 16),
      axis.text = element_text(size = 14),
      axis.title = element_text(size = 14),
      legend.position = "none"
    )

b = create_time_plots("Negative symptom")
(b/a) +
  plot_layout(heights = c(1, 1,1)) +
  plot_annotation(
    title = "Negative Symptoms",
    subtitle = "Like emotional flatness, low motivation, social withdrawal, distractibility, and difficulty expressing emotions.",
    caption = "0 = Not at all, 100 = Constantly",
    theme = theme(
      plot.title = element_text(size = 18, face = "bold"),
      plot.subtitle = element_text(size = 14),
      plot.caption = element_text(size = 14)
    )
  )

```

#### Average Ratings by Question (Over the Past 4 Hours)

```{r echo=FALSE, fig.height=3, fig.width=11.5, message=FALSE, warning=FALSE}
ggplot(item_means[item_means$ema_category == "Negative symptom",], aes(x = reorder(questionText, mean_response), y = mean_response)) +
  geom_col(width = 0.6, fill = color3) +
  coord_flip() +
 # scale_fill_manual(values = category_colors) +
  labs(
    x = NULL,
    y = ""
  ) +
  ylim(c(0,100)) +
  theme_minimal() +
   theme(
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 16),
      legend.position = "none"
    )


```

```{r echo=FALSE, fig.height=6.5, fig.width=11.5, message=FALSE, warning=FALSE}
a = ggplot(category_means[category_means$ema_category == "Functional outcome",], aes(x = date, y = mean_response, color = color2)) +
  scale_color_manual(values = color2) +
  geom_line() +
  scale_y_continuous(
    limits = c(0, 100)
  )  +
  scale_color_manual(values = color2) +
  labs(
    title = "Variation Over Time (Average per Day)",
    y = "",
    x = ""
  ) +
  theme_minimal() +
   theme(
      plot.title = element_text(face = "bold", size = 16),
      axis.text = element_text(size = 14),
      axis.title = element_text(size = 14),
      legend.position = "none"
    )

b = create_time_plots("Functional outcome")
(b/a) +
  plot_layout(heights = c(1, 1,1)) +
  plot_annotation(
    title = "Everyday Activities",
    subtitle = "Like being able to manage health, interacting with others, and completing daily activities.",
    caption = "0 = Not at all, 100 = Constantly",
    theme = theme(
      plot.title = element_text(size = 18, face = "bold"),
      plot.subtitle = element_text(size = 14),
      plot.caption = element_text(size = 14)
    )
  )

```

#### Average Ratings by Question (Over the Past 4 Hours)

```{r echo=FALSE, fig.height=3, fig.width=11.5, message=FALSE, warning=FALSE}


ggplot(item_means[item_means$ema_category == "Functional outcome",], aes(x = reorder(questionText, mean_response), y = mean_response)) +
  geom_col(width = 0.6, fill = color3) +
  coord_flip() +
 # scale_fill_manual(values = category_colors) +
  labs(
    x = NULL,
    y = ""
  ) +
  ylim(c(0,100)) +
  theme_minimal() +
 theme(
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 16),
      legend.position = "none"
    )

sleep = df_filtered[df_filtered$ema_category == "Sleep quality",]

```

### 🌙 Sleep

`r glue::glue("You told us about your sleep quality by rating how much trouble you had sleeping last night. On average, you rated your trouble sleeping as **{round(mean(as.numeric(sleep$response), na.rm = TRUE))} out of 100**.")`

```{r echo=FALSE, fig.height=2.5, fig.width=11.5, message=FALSE, warning=FALSE}

ggplot(sleep, aes(x = as.Date(date), y = as.numeric(response))) +
  geom_line(color = color1) +  # point color
 # geom_smooth(method = "loess", se = FALSE, size = 1.2, color = "#1B3B5F") +  # line color
  scale_y_continuous(
    limits = c(0, 100)
  ) +
  scale_x_date(name = "Date") +
  labs(
    title = "Sleep Quality",
    subtitle = "Last night I had trouble with sleep (0 = Not at all, 100 = Constantly)",
    y = ""
  ) +
  theme_minimal() +
   theme(
      plot.title = element_text(face = "bold", size = 16),
      axis.text = element_text(size = 14),
      axis.title = element_text(size = 14),
      legend.position = "none"
    )


```

## 📅 How You Felt Each Week

Throughout the study, you filled out **weekly questionnaires**. This section summarizes which answers you gave. 

```{r echo=FALSE,comment=""}
# Define PANAS labels and type
panas_labels <- c(
  "Interested", "Distressed", "Excited", "Upset", "Strong",
  "Guilty", "Scared", "Hostile", "Enthusiastic", "Proud",
  "Irritable", "Alert", "Ashamed", "Inspired", "Nervous",
  "Determined", "Attentive", "Jittery", "Active", "Afraid"
)

mood_type <- ifelse(panas_labels %in% c(
  "Interested", "Excited", "Strong", "Enthusiastic", "Proud",
  "Alert", "Inspired", "Determined", "Attentive", "Active"),
  "Positive", "Negative"
)

if (exists("weekly") && nrow(weekly) > 0) {
  # Add week labels
  weekly <- weekly %>%
    mutate(week = factor(redcap_event_name,
                         levels = unique(redcap_event_name[order(redcap_event_name)]),
                         labels = paste("Week", seq_along(unique(redcap_event_name)))))
  
  # Long format + mood type
  long_data <- weekly %>%
    pivot_longer(cols = starts_with("panas_"),
                 names_to = "item", values_to = "value") %>%
    mutate(value = as.numeric(value),
           item_num = as.numeric(gsub("panas_", "", item)),
           label = panas_labels[item_num],
           mood = mood_type[item_num])
  library(dplyr)
  
  # Calculate mean ratings per emotion across all weeks
  summary_stats <- long_data[long_data$mood == "Positive",] %>%
    group_by(label) %>%
    summarise(mean_rating = mean(value, na.rm = TRUE)) %>%
    arrange(desc(mean_rating))
  
  # Get strongest and weakest emotions
  strongest_emotion <- summary_stats$label[1]
  strongest_value <- round(summary_stats$mean_rating[1], 2)
  
  weakest_emotion <- summary_stats$label[nrow(summary_stats)]
  weakest_value <- round(summary_stats$mean_rating[nrow(summary_stats)], 2)
  } else {
      # No weekly data
      long_data <- NULL
      pos_stats <- NULL
      neg_stats <- NULL
  }
```

#### Positive Emotions

First, we will look at your positive emotions throughout the past few
weeks.
`r glue::glue("Across all weeks, the strongest positive emotion reported was **{strongest_emotion}**. The weakest average emotion was **{weakest_emotion}**.")`

```{r echo=FALSE, fig.height=8.5, fig.width=11.5, message=FALSE, warning=FALSE}

plot_mood <- function(data,mood_type_title) {
# Prepare average values and frequency for ordering
avg_values <- data %>%
  group_by(label) %>%
  summarize(
    avg_value = mean(value, na.rm = TRUE),
  ) %>%
  arrange(desc(avg_value)) %>%
  mutate(label = factor(label, levels = unique(label)))  # Order by frequency

# Then apply the same ordering to the main data for the line plot:
data <- data %>%
  mutate(label = factor(label, levels = levels(avg_values$label)))
 
p_line <- ggplot(data, aes(x = as.Date(w_timestamp), y = value, group = 1)) +
    geom_line(color = color1, size = 1) +
    geom_point(color = color1, size = 2) +
    facet_wrap(~ label, scales = "fixed", ncol = 1) +
    scale_y_continuous(
      limits = c(1, 5),
      breaks = c(1, 5),
      labels = c("Very slightly/ Not at all", "Extremely")
    ) +
    labs(title = "", y = NULL, x = NULL) +
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      panel.grid.minor = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.title.x = element_text(size = 12),
      strip.text = element_text(face = "bold", size = 12),
      axis.ticks.x = element_line(),
      strip.placement = "inside",
    )

#avg_values$label <- factor(avg_values$label, levels = rev(levels(avg_values$label)))

round_to_custom <- function(x, vec = c(1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5)) {
  sapply(x, function(xi) vec[which.min(abs(vec - xi))])
}

avg_values <- avg_values %>%
  mutate(
    rounded_val = round_to_custom(avg_value),
    desc = case_when(
      rounded_val == 1 ~ "very slightly or not at all",
      rounded_val == 1.5 ~ "very slightly to a little",
      rounded_val == 2 ~ "a little",
      rounded_val == 2.5 ~ "a little to moderately",
      rounded_val == 3 ~ "moderately",
      rounded_val == 3.5 ~ "moderately to quite a bit",
      rounded_val == 4 ~ "quite a bit",
      rounded_val == 4.5 ~ "quite a bit to extremely",
      rounded_val == 5 ~ "extremely",
      TRUE ~ "unknown"
    ),
    label_text = str_c("...on average ", desc, "\n", tolower(label))
  )


plot_mood_bar <- ggplot(avg_values, aes(x = avg_value, y = "test")) +
 # geom_bar(fill = "#1B4332", width = 0.7, stat = "identity") +
  geom_text(aes(label = label_text, x = 0.01),
            hjust = 0, size = 4, color = "black") +
  facet_wrap(~ label, scales = "fixed", ncol = 1) +
  xlim(0, 5) +  # extend limit to make space for text
  labs(title = "", x = NULL, y = NULL) +
  theme_void() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    strip.text = element_text(color = "white", face = "bold", size = 12)
  )

  combined_plot <- p_line + plot_mood_bar + plot_layout(widths = c(2, 1.5)) + plot_annotation(
    title = paste(mood_type_title),
    theme = theme(
      plot.title = element_text(size = 18, face = "bold", hjust = 0.5)
    ))
  
  return(combined_plot)

}


# Now generate the plots
if (!is.null(long_data)) {
positive_plot <- plot_mood(filter(long_data, mood == "Positive"), "Positive Emotions")
negative_plot <- plot_mood(filter(long_data, mood == "Negative"), "Negative Emotions")
positive_plot

} else {
  cat("No weekly data available for  emotions.\n")
}

```

```{r echo=FALSE, comment=""}
# Define PANAS labels and type
panas_labels <- c(
  "Interested", "Distressed", "Excited", "Upset", "Strong",
  "Guilty", "Scared", "Hostile", "Enthusiastic", "Proud",
  "Irritable", "Alert", "Ashamed", "Inspired", "Nervous",
  "Determined", "Attentive", "Jittery", "Active", "Afraid"
)

mood_type <- ifelse(panas_labels %in% c(
  "Interested", "Excited", "Strong", "Enthusiastic", "Proud",
  "Alert", "Inspired", "Determined", "Attentive", "Active"),
  "Positive", "Negative"
)

long_data <- NULL
neg_stats <- NULL
strongest_emotion <- NA
weakest_emotion <- NA

if (exists("weekly") && nrow(weekly) > 0) {
# Add week labels
weekly <- weekly %>%
  mutate(week = factor(redcap_event_name,
                       levels = unique(redcap_event_name[order(redcap_event_name)]),
                       labels = paste("Week", seq_along(unique(redcap_event_name)))))

# Long format + mood type
long_data <- weekly %>%
  pivot_longer(cols = starts_with("panas_"),
               names_to = "item", values_to = "value") %>%
  mutate(item_num = as.numeric(gsub("panas_", "", item)),
         label = panas_labels[item_num],
         mood = mood_type[item_num])
library(dplyr)

# Calculate mean ratings per emotion across all weeks
summary_stats <- long_data[long_data$mood == "Negative",] %>%
  group_by(label) %>%
  summarise(mean_rating = mean(value, na.rm = TRUE)) %>%
  arrange(desc(mean_rating))

# Get strongest and weakest emotions
strongest_emotion <- summary_stats$label[1]
strongest_value <- round(summary_stats$mean_rating[1], 2)

weakest_emotion <- summary_stats$label[nrow(summary_stats)]
weakest_value <- round(summary_stats$mean_rating[nrow(summary_stats)], 2)
}

```

\newpage

#### Negative Emotions

Now we will look at your negative emotions during the past few weeks.
`r glue::glue("Across all weeks, the strongest negative emotion reported was **{strongest_emotion}**. The weakest average emotion was **{weakest_emotion}**.")`

```{r echo=FALSE, fig.height=8.5, fig.width=10, message=FALSE, warning=FALSE}

if (!is.null(long_data)) {
negative_plot

} else {
  cat("No weekly data available for emotions.\n")
}

```

\newpage

### Your Weekly Life Events

Each week, we asked you to share both positive and challenging
experiences. Below is a summary of the types of events you reported
**over all study weeks** and how frequently they came up. Words that
appear larger were mentioned more often.

```{r echo=FALSE, fig.height=5, fig.width=10, message=FALSE, warning=FALSE}
# Create a corpus and clean it
if (exists("weekly") && nrow(weekly) > 0) {
corpus <- Corpus(VectorSource(weekly$life))
corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeWords, stopwords("en"))

# Create term-document matrix
tdm <- TermDocumentMatrix(corpus)
matrix <- as.matrix(tdm)
word_freqs <- sort(rowSums(matrix), decreasing=TRUE)
df <- data.frame(word = names(word_freqs), freq = word_freqs)

# Custom color palette
my_colors <- c("#00331A","#00693E", "#228B22", "#CBA135")

# Generate word cloud
set.seed(123) # for reproducibility
wordcloud(words = df$word,
          freq = df$freq,
          scale = c(4, 0.8),
          min.freq = 1,
          max.words = 100,
          random.order = FALSE,
          rot.per = 0.1,
          colors = my_colors)
}
```
